The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-13 manuscript.Rmd
[fix #81, fix #82] revisit latitudinal gradient

```{r latitudinal-gradient, fig.cap='Latitudinal gradient in species richness for the Pacific and Atlantic oceans (Gulf of Mexico records excluded). Trend lines are B-splines of the 3rd degree polynomial weighted by the square-root of the number of records. (\\#fig:latitudinal-gradient)'}
knitr::include_graphics("figures/combined_gradient.pdf")
```

@@

<!-- include results earlier? -->

>>>>

```{r latitudinal-gradient, fig.cap='Latitudinal gradient in species richness for the Pacific and Atlantic oceans (Gulf of Mexico records excluded), based on inferred species richness (A) and recorded species richness (B). The patterns are strongly influenced by the sampling effort (C). Trend lines are rolling means with a window of size of 3. (\\#fig:latitudinal-gradient)'}
knitr::include_graphics("figures/gradient.pdf")
```

@@

To infer the number of species along the latitudinal gradient (Fig. \@ref(fig:latitudinal-gradient)), we estimated the species ranges by using the southernmost and northernmost observations for each species on the Atlantic and Pacific coast separately. Records for the Gulf of Mexico were not included in this analysis.
